---
title: "package_creator"
author: "Ramon Crespo"
date: "12/5/2018"
output: html_document
---
The objective of this code is to compile some of the needed steps to generate a package in R. It is the simplest way I have of making this work. As we get more complicated we could start adding some more things. 

Step 1
Import the necessary libraries and create the working folder
```{r setup, include=FALSE}
library("devtools")
library(roxygen2)

setwd("~/repos/ars/")
create("pack")
```

Step 2
The function below just works as a way of moving the latest document into the R package
```{r}
file.copy("~/repos/ars/code-sketch-12-04-2018.R", "~/repos/ars/pack/R/" )
```

Step 3
Add comments usin roxygen 
The format we will use will be the following

#' Title ( Example:Illustration of crayon colors)
#'
#' Description (Creates a plot of the crayon colors in \code{\link{brocolors}})
#'
#' @param method2order method to order colors (\code{"hsv"} or \code{"cluster"})
#' @param cex character expansion for the text
#' @param mar margin parameters; vector of length 4 (see \code{\link[graphics]{par}})
#'
#' @return None
#'
#' @examples
#' plot_crayons()
#'
#' @export

```{r}
setwd("~/repos/stat243/pack")
document()
```


```{r}
install("pack")
?ars
ars()
```

